Updates on the Exoplanet Orbit Database

### 2013-12-27 draft/ms.tex
Add parameter table and list all parameters

%\documentclass{emulateapj}
% Requirement of PASP to use preprint and aastex
\documentclass[12pt,preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

@@

\end{CJK*}

>>>>

%\documentclass{emulateapj}
% Requirement of PASP to use preprint and aastex
\documentclass[11pt,preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table
\clearpage

\begin{deluxetable}{llll}
\tabletypesize{\scriptsize}
\rotate
\tablewidth{0pt}
\tablecaption{Fields of Exoplanet Orbit Database}
\tablehead{
  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{a}}
}
\startdata
\sidehead{\textbf{Planet Information}}
NAME\dotfill & String & Name of planet &  \\
OTHERNAME\dotfill & String & Other commonly used name of planet &  \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) &  \\
HD\dotfill & String & &  \\
HR\dotfill & String & &  \\
HIPP\dotfill & String & & \\
SAO\dotfill & & & \\
GL\dotfill & & & \\
BINARY\dotfill & & & BINARYREF BINARYURL \\
RA, RA\_STRING\dotfill & & & \\
DEC, DEC\_STRING\dotfill & & & \\
KEPID\dotfill & & & \\
KOI\dotfill & & & \\
KDE\dotfill & & & \\
EOD\dotfill & & & \\
MICROLENSING\dotfill & & & \\ 
IMAGING\dotfill & & & \\
TIMING\dotfill & & & \\
ASTROMETRY\dotfill & & & \\
\sidehead{\textbf{Stellar Parameters}}
BMV\dotfill & & & \\
V\dotfill & & & VREF,VURL \\
J\dotfill & & & \\
H\dotfill & & & \\
KS\dotfill & & & \\
DIST\dotfill & & & DISTUPPER,DISTLOWER,UDIST,DISTREF,DISTURL \\
PAR\dotfill & & & PARUPPER,PARLOWER,UPAR \\
VSINI\dotfill & & & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
GAMMA\dotfill & & & GAMMAUPPER,GAMMALOWER,UGAMMA,GAMMAREF,GAMMAURL \\
\sidehead{\textbf{Orbit Parameters}}
PER\dotfill & & & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
ECC\dotfill & & & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
OM\dotfill & & & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
K\dotfill & & & KUPPER,KLOWER,UK,KREF,KURL \\
T0\dotfill & & & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
DVDT\dotfill & & & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
I\dotfill & & & IUPPER,ILOWER,UI,IREF,IURL \\
MSINI\dotfill & & & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
A\dotfill & & & AUPPER,ALOWER,UA,AREF,AURL \\
MASS\dotfill & & & MASSUPPER,MASSLOWER,UMASS,MASSREF,MASSURL \\
SEP\dotfill & & & SEPUPPER,SEPLOWER,USEP,SEPREF,SEPURL \\
TREND\dotfill  & & & \\
LAMBDA\dotfill & & & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
BIGOM\dotfill & & & BIGOMUPPER,BIGOMLOWER,UBIGOM,BIGOMREF,BIGOMURL \\
FREEZE\_ECC\dotfill & & & \\
\sidehead{\textbf{Transit Parameters}}
DEPTH\dotfill & & & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
T14\dotfill & & & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
TT\dotfill & & & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
R\dotfill & & & RUPPER,RLOWER,UR,RREF,RURL \\
AR\dotfill & & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
B\dotfill & & & BUPPER,BLOWER,UB,BREF,BURL \\
DENSITY\dotfill & & &
DENSITYUPPER,DENSITYLOWER,UDENSITY,DENSITYREF,DENSITYURL \\
GRAVITY\dotfill & & &
GRAVITYUPPER,GRAVITYLOWER,UGRAVITY,GRAVITYREF,GRAVITYURL \\
TRANSIT\dotfill & & & TRANSITREF,TRANSITURL \\
DR\dotfill & & & DRUPPER,DRLOWER,UDR,DRREF,DRURL \\
RR\dotfill & & & RRUPPER,RRLOWER,URR,RRREF,RRURL \\
\sidehead{\textbf{Secondary Eclipse}}
SE\dotfill & & & SEREF,SEURL \\
SEDEPTHJ\dotfill & & &
SEDEPTHJUPPER,SEDEPTHJLOWER,USEDEPTHJ,SEDEPTHJREF,SEDEPTHJURL \\
SEDEPTHH\dotfill & & &
SEDEPTHHUPPER,SEDEPTHHLOWER,USEDEPTHH,SEDEPTHHREF,SEDEPTHHURL \\
SEDEPTHKS\dotfill & & &
SEDEPTHKSUPPER,SEDEPTHKSLOWER,USEDEPTHKS,SEDEPTHKSREF,SEDEPTHKSURL \\
SEDEPTHKP\dotfill & & &
SEDEPTHKPUPPER,SEDEPTHKPLOWER,USEDEPTHKP,SEDEPTHKPREF,SEDEPTHKPURL \\
SEDEPTH36\dotfill & & &
SEDEPTH36UPPER,SEDEPTH36LOWER,USEDEPTH36,SEDEPTH36REF,SEDEPTH36URL \\
SEDEPTH45\dotfill & & &
SEDEPTH45UPPER,SEDEPTH45LOWER,USEDEPTH45,SEDEPTH45REF,SEDEPTH45URL \\
SEDEPTH58\dotfill & & & 
SEDEPTH58UPPER,SEDEPTH58LOWER,USEDEPTH58,SEDEPTH58REF,SEDEPTH58URL \\
SEDEPTH80\dotfill & & &
SEDEPTH80UPPER,SEDEPTH80LOWER,USEDEPTH80,SEDEPTH80REF,SEDEPTH80URL \\
SET\dotfill & & & SETUPPER,SETLOWER,USET,SETREF,SETURL \\
\sidehead{\textbf{Fit \& References}}
RMS\dotfill & & & \\
CHI2\dotfill & & & \\
NOBS\dotfill & & & \\
NCOMP\dotfill & & & \\
MULT\dotfill & & & \\
PLANETDISCMETH\dotfill & & & \\
STARDISCMETH\dotfill & & & \\
DATE\dotfill & & & \\
FIRSTREF\dotfill & & & FIRSTURL \\
ORBREF\dotfill & & & ORBURL \\
\sidehead{\textbf{Stellar Properties}}
STAR\dotfill & & & \\
MSTAR\dotfill & & & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
RSTAR\dotfill & & & RSTARUPPER,RSTARLOWER,URSTAR,RSTARREF,RSTARURL \\
TEFF\dotfill & & & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\
RHOSTAR\dotfill & & &
RHOSTARUPPER,RHOSTARLOWER,URHOSTAR,RHOSTARREF,RHOSTARURL \\
LOGG\dotfill & & & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
FE\dotfill & & & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
SHK\dotfill & & & \\
RHK\dotfill & & & \\
KP\dotfill & & & \\
SPECREF\dotfill & & & SPECURL \\
\sidehead{\textbf{Links}}
JSNAME\dotfill & & & EPEURL \\
ETDNAME\dotfill & & & ETDURL \\
SIMBADNAME\dotfill & & & SIMBADURL \\
EANAME\dotfill & & & EAURL \\
\enddata
\tablenotetext{a}{XU, XUPPER, XLOWER, XREF, XURL etc.}
\end{deluxetable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{CJK*}
